---
title: "Group 3 — Bodies and talk"
subtitle: "Studio wall"
author: "Group names here"
format:
  html:
    toc: true
    toc-depth: 2
---

# Spine

> How do bodies measure, how do people talk about mind and school, and how long do countries live?

This sentence stays at the top. Every panel must attach to it. If a plot cannot be introduced in a clause that hangs off this line, it is off the wall.

# Introduction — the tables we own
```{r}
library(ggformula)
library(skimr)
library(tidyverse)
library(mosaic)
```

This folder is ours for the ten days. Three tables, three shapes.

- **Panel A** (`panel-A.csv`) — body measures (`bdims`): height, weight, waist, hip, chest, age, sex. Stand-in for NHANES when that package is not on the machine.
- **Panel B** (`panel-B.csv`) — GSS 2010: `degree`, `grass`, hours of work and rest. `mntlhlth` is *days* of poor mental health — a Quant. Do not mosaic it.
- **Panel C** (`panel-C.csv`) — gapminder 2007: life expectancy, GDP per capita, population by country.

Talk (B) and tape-measure (A) are different hunts.

We load from this folder:


```{r}
library(skimr)
library(tidyverse)
library(ggformula)
```

A <- read_csv("panel-A.csv")
```

```
```{r}
panel_A <- read_csv("data/panel-A.csv")
panel_C <- read_csv("data/panel-C.csv")
```

Found tables train the mark. A campus Free Hunch, if we collect one, is a **made** panel of the same pair type — new people, old grammar. It does not replace A, B, or C.

# Panel A — body / measure

*height_cm, weight_kg, waist_cm are Quant. sex is Qual.*


### 1. See the table

We have 6 quantitative variables in our data - age, weight_kg, height_cm, waist_cm, hip_cm, chest_cm.
We have 1 quantitative variable - sex.

```{r}
glimpse(panel_A)
skim(panel_A)
inspect(panel_A)
```

### 2. Ask

One question this table can answer. One it cannot. Write both.

Who is heavier between men and women ?
What is the proportion of men and women ?
How does waist size vary for men and women ?
How does hip size vary for men and women ?
How does chest size vary for men and women ?

### 3. Choose a mark

Who is heavier between men and women ?
-Histogram 

What is the proportion of men and women ?
-Bar

How does waist size vary for men and women ?
-Histogram

How does hip size vary for men and women ?
-Density

How does chest size vary for men and women ?
-Density

Which sex is older in the given data-set ?
-Histogram

Who is taller between men and women ?
-Histogram

### 4. Predict

We predicted that the graph would depict the chest size and the hip size of women to be more than men.
Referring to the stereotypical anatomy, we predict the variation in chest size and hip size of women to be more than men.

### 5. Make

Who is heavier between men and women?
```{r}
panel_A |> gf_histogram(~weight_kg,fill =~sex,bins = 50)
```

What is the proportion of men and women?
```{r}
panel_A |> gf_bar(~sex,fill=~sex)
```

How does waist size vary for men and women?
```{r}
panel_A |> gf_histogram(~waist_cm,fill=~sex)
```

How does hip size vary for men and women ?
```{r}
panel_A |> gf_density(~hip_cm,fill=~sex)
```

How does chest size vary for men and women ?
```{r}
panel_A |> gf_density(~chest_cm,fill=~sex)
```

How does age vary for men and women?
```{r}
panel_A |> gf_bar(~ age, fill = ~ sex)
```

How does height vary for men and women?
```{r}
panel_A |> gf_histogram(~height_cm,fill =~sex,bins = 50)
```

How does age vary across the data-set?
```{r}
panel_A |> gf_bar(~ age,)
```

How does weight vary across the data-set?
```{r}
panel_A |> gf_density(~weight_kg)
```

How does height vary across the data-set?
```{r}
panel_A |> gf_density(~ height_cm,)
```

How does waist size vary across the data-set?
```{r}
panel_A |> gf_density(~ waist_cm,)
```

How does hip size vary across the data-set?
```{r}
panel_A |> gf_density(~ hip_cm,)
```

How does chest size vary across the data-set?
```{r}
panel_A |> gf_density(~ chest_cm)
```


### 6. Say

We all found the density graph comparing chest sizes of men and women interesting  because according to the graph, men have a bigger chest size than women which is quite unexpected. Men also have larger variation in the sizes while women have more difference in density for different sizes.
This is surprising because according to the bar graph, the ratio of women is slightly more than men, in comparison.
We also found the density graph comparing hip size of men and women surprising because it is contrasting the general belief that women have wider hips.

### 7. Limit
```{r}
panel_A |> group_by(sex) |> summarize (mean_chest_cm = mean(chest_cm, na.rm = T))
```


```{r}
mosaic::t_test(chest_cm ~ sex, data = panel_A)
```

# Panel B — category / talk

degree × grass is Qual + Qual. mntlhlth is Quant — it belongs in a histogram or a grouped violin, not a mosaic.

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

The quantitative variables in  the dataset are -hours of relaxation(hrsrelax), hours of labour (hrsl) and mental health(mntlhlth) {3}
The qualitative variables in  the dataset are-degree, marijuana(grass) {2}

We have 2 qualitative variables - degree [education] and grass [marijuana].
We have 3 quantitative variables - mntlhlth [mental health], hrsl [hours of labour], hrsrelax [hours of relaxation]

```{r}
panel_B <- read_csv("data/panel-B.csv")
```


```{r}
glimpse(panel_B)
inspect(panel_B)
skim(panel_B)
```


### 2. Ask

Does the education of a person affect their opinions on whether grass should be legal or not?


### 3. Choose a mark

Does the education of a person affect their opinions on whether grass should be legal or not?
- Mosaic Graph

### 4. Predict

we predict that a person pursuing a higher education degree would want marijuana to be legal, to regulate stress levels and mental health.

### 5. Make

```{r}
panelB_mod <- panel_B |> drop_na(grass)
```

```{r}
dim(panelB_mod)
```

```{r}
vcd::structable(degree~grass, data = panel_B)
```

```{r}
vcd::structable(degree ~ grass, data = panel_B )
```

```{r}
vcd::structable(degree~grass, data=panel_B) |>
  vcd::mosaic(labeling_args = list(rot_labels = c(top = 45)),
              margins = c(top = 6))
```
```{r}
vcd::structable(degree~grass,data=panel_B) |> vcd :: mosaic(type="expected",labeling_args = list(rot_labels = c(top = 45)),margins = c(top = 6))
```



### 6. Say

Looking at the graph, the ratio of people who think marijuana should be legal and not legal appears to be similar, in each individual degree. 
Saying that, it is surprising information to see that the percentage of high schoolers who want marijuana to be legal is way larger than any other degrees.
But this could also be because the number of high schoolers in this dataset is much more.

### 7. Limit

```{r}
mosaic::xchisq.test(degree~grass, data=panel_B)
```

# Panel C — place

*lifeExp is the honest fill. pop is a count — symbol map, not choropleth.*

Geometry is not in the CSV. Join in R, then use the same seven headings.

```r
# library(sf)
# library(rnaturalearth)
# world <- ne_countries(scale = "medium", returnclass = "sf")
# # join on country name; list the unmatched labels
```


### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

```r
# glimpse() / inspect() / skim()
```

### 2. Ask

One question *this* table can answer. One it cannot. Write both.

### 3. Choose a mark

Geom, map mark, or (later) test that matches the pair type. Name it before you code.

### 4. Predict

What do we think we will see? One sentence, before Run.

### 5. Make

Human brick first. Optional: one AI prompt, pasted below, only for what section 3 named.

```r
# human chunk

# ## Prompt we actually used
# ai_draft
# ours
```

### 6. Say

Caption + one sentence we will stand behind. Title is a sentence, not a column name.

### 7. Limit

What this panel cannot do. Which kit table we refused to abuse.


# Conclusion

What the spine looks like after three panels.

- The question we will defend in ninety seconds
- What we will **not** claim
- Which lines were human, which were machine
- Limits: sample, missingness, the test we did not run
- Gift for the steal-this strip (palette, annotation, join trick)

```r
# sessionInfo()
```



